Figures

### 2019-04-08 code/figures.rmd
Added r (point-biserial) tau2 figure and caching options

```{r MA_df}
summarizer <- function(x){
  fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, data = x) #takes raw correlation as input
  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1)) #estimates out
}
#Default method of metafor for calculating H2 is truncated at one. Alternative method for calculating H2 provides information also on excessive homogeneity, i.e, less variability than expected by chance (that is, does not have a lower limit of 1). This method approximates H2 as if we were using the Dersimonian and Laird estimate of tau2, although we use REML. See Higgins & Thompson, 2002 and ?print.rma.uni.

@@

res2 <- res %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect") %>% 
  mutate(z = abs(z)) #Absolute values since we are interested in effect size rather than direction
```

```{r cor_het_z}
#Basic correlations
cor.test(res2$I2, res2$z) #pearson

I2_fit <- summary(lm(I2 ~ z, data = res2))

cor.test(res2$H2, res2$z) #pearson

@@

```{r plot_res}

I2 <- ggplot(res2, aes(x = z, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  xlab("Fisher's z") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.15, y = 80, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z), ")")))

H2 <- ggplot(res2, aes(x = z, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  xlab("Fisher's z") +
  geom_text(x = 0.14, y = 5.9, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z),")")))

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
effect_het
save_plot("../figures/effect-het.png", effect_het,
          nrow = 2, base_height = 5, base_width = 5, dpi = 600)

@@

```{r Plot_tau_against_I2, fig.asp = 0.618}
dat3 <- readRDS("../data/tau_simulation_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

```{r Density_plot, fig.asp= 0.618}
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))

>>>>

```{r MA_df}
summarizer <- function(x){
  fit <- rma(measure = "ZCOR", ri = x$r, ni = x$n, data = x) #takes raw correlation as input
  fitr <- rma(measure = "COR", ri = x$r, ni = x$n, data = x)
  data.frame(z = fit$b[[1]], I2 = fit$I2, H2trunc = fit$H2, H2 = fit$QE / (fit$k - 1),
             r = fitr$b[[1]], tau2r = fitr$I2) #estimates out
}
#Default method of metafor for calculating H2 is truncated at one. Alternative method for calculating H2 provides information also on excessive homogeneity, i.e, less variability than expected by chance (that is, does not have a lower limit of 1). This method approximates H2 as if we were using the Dersimonian and Laird estimate of tau2, although we use REML. See Higgins & Thompson, 2002 and ?print.rma.uni.

@@

res2 <- res %>% 
  split(.$effect) %>%  #separate by effect, necessary step otherwise the function is applied overall
  map_dfr(summarizer, .id = "effect") %>% 
  mutate(z = abs(z), r = abs(r)) #Absolute values since we are interested in effect size rather than direction
```

```{r cor_het_effect_size, results = "hide", cache=TRUE}
#Basic correlations
cor.test(res2$I2, res2$z) #pearson I2

I2_fit <- summary(lm(I2 ~ z, data = res2)) #for annotating figures

cor.test(res2$tau2r, res2$r) #pearson tau2

tau2_fit <- summary(lm(tau2r ~ r, data = res2))

cor.test(res2$H2, res2$z) #pearson H2

@@

```{r plot_res, cache = TRUE}

I2 <- ggplot(res2, aes(x = z, y = I2)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  coord_cartesian(ylim = c(0, 100)) +
  geom_text(x = 0.15, y = 80, fontface = "italic", size = 3.5, label = paste0("b = ", format(round(I2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(I2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(I)^2," index"))) +
  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z), ")")))

H2 <- ggplot(res2, aes(x = z, y = H2)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = 5.9, size = 3.5, fontface = "italic", label = paste("b = ", format(round(H2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(H2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste(italic(H)^2," index", sep = ""))) +
  scale_x_continuous(name = expression(paste("Effect size (Fisher's ", italic(z),")")))

effect_het <- plot_grid(I2, H2, nrow = 2, labels = c("a", "b"), align = "v") #combine plots
effect_het
#save_plot("../figures/effect-het.png", effect_het,
#          nrow = 2, base_height = 5, base_width = 5, dpi = 600)

@@

```{r r_vs_tau2, fig.asp = 0.618, cache = TRUE}
r_tau2 <- ggplot(res2, aes(x = r, y = tau2r)) + 
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", se = TRUE, color = "black") +
  geom_text(x = 0.14, y = 75, size = 3.5, fontface = "italic", label = paste("b = ", format(round(tau2_fit$coefficients[2, 1], 2), nsmall = 2), ", r = ", format(round(sqrt(tau2_fit$r.squared), 2), nsmall = 2))) +
  theme_classic() +
  scale_y_continuous(name = expression(paste("Between studies variance ", italic(tau)^2))) +
  scale_x_continuous(name = expression(paste("Point-biserial correlation ", italic(r))))

r_tau2
# ggsave("../figures/r_tau2.png", dpi = 600, height =  4 , width = 6.47)

```{r Plot_tau_against_I2, fig.asp = 0.618, cache = TRUE}
dat3 <- readRDS("../data/tau_simulation_results.RDS")
names(dat3) <- sort(unique(dat$effect)) #names were alphabetized upon splitting in simulation so must sort

@@

```{r Density_plot, fig.asp= 0.618, cache = TRUE}
dens <- readRDS("../data/power_simulation_results.RDS")
names(dens) <-  sort(unique(dat$effect))
